---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: Woo Hyeon Her
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_orig, aes(x = State, y = Cases_Total)) + geom_point() + theme(axis.text.x = element_text(angle = 90))
```
```{r letsgo}
ggplot(covid_data_count, aes(x = state, y = Cases, color = race)) + geom_point() + theme(axis.text.x = element_text(angle = 90))
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```
``` {r plotttt}
covid_data_count |> filter(state == "AK") |> ggplot(aes(x = race, y = Cases)) + geom_point()
```


1. Write code for a plot and describe what you observe?

```{r Question 1}
ggplot(covid_data_count, aes(x = state, y = Cases, color = race)) + geom_point() + theme(axis.text.x = element_text(angle = 45, vjust=0.5))
```
In the plot I made above, I observe that there are some states with higher cases than other states. For example, states such as CA, FL, NY, and TX have more recorded cases than other states. 

2. Are there any conclusions you can draw?
I think what we can draw here is that population and observed cases have correlation between them. Generally, states with higher populations have higher observed cases.

3. What were you not able to do due to not having the R knowledge?
I wanted to filter out "Total" from the race but was not able to. Unfortunately I did not have knowledge to do so.

4. What other data would be useful to better understand this data?
It would be good to have data on how many people were cured from COVID to better identify which states dealt with the situation better.
